Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-14 chapters/analysis_techniques.tex
Changes 1. Added more visualizations of data 2. Added some images of analysis techniques in use 3. Fixed referencing to some images in aims 1,2,3

>>>>

\subsection{Interface order}
\label{section:interface_order}

We can calculate the ordering of the interface from the iso-surface of the interface. The simulation data was first pre-processed by calculating the 
order parameter of the densities, $\phi$. We then apply the particle filling algorithm described in section \ref{section:filling_routine} 
to the $\phi$ distribution. We then mesh the filled order parameter at $\phi = 0$ using the marching cubes algorithm and obtain the normals of the
vertices representing the points of the interface. We then computed the interfacial orientation tensor and plot that 
%
\begin{equation}
\tens{Q}_{\text{int}} = \frac{1}{\langle \mathrm{tr}(\tens{A}) \rangle} 
\left\langle \tens{A} - \frac{1}{3} \mathrm{tr}(\tens{A}) \mathsf{1} \right\rangle ,
\end{equation}
%
where the local tensor field $\tens{A}$ is defined by
%
\begin{equation}
\tens{A} = \nabla\phi\otimes\nabla\phi .
\end{equation}
%
The largest eigenvalue of $\tens{Q}$ is taken as the
interface nematic order parameter $S_{\text{int}}$.

\subsection{Channel size distribution}
\label{section:channel_size_distribution}

We use a method based on that outlined in Chan and Thornton. We create our distance function by performing an Eularian Distance Transform on 
our order parameter data $\phi$ to obtain $\phi_{edt}$. \cite{chan_channel_2012} We smooth $\phi_{edt}$ using a boxcar algorithm with side length 3. 
We then normalize the distance from the interface in $\phi_{edt}$ using the characteristic length scale of the system defined as $\Sigma = \frac{V}{A_{int}}$
to obtain $\bar{\phi}_{edt}$ and a normalized distance from the interface, $\bar{r}$. A schematic of this workflow is demonstrated in Figure \ref{fig:csd_prep_viz}.

\begin{figure}
    \centering
    \includegraphics[scale = 0.4]{figures/analysis/csd_prep.png}
    \caption{Schematics detailing the order of operations of the steps to calculate the channel size distribution.}
    \label{fig:csd_prep_viz}
\end{figure}

The number of handles, $h$
in the iso-surface at different distances from the interface of $\bar{\phi}_{edt}$ is calculated. $h$ is also normalized by $\Sigma$ and the system volume
to obtain $\bar{h} = \frac{h}{V\Sigma^{-3}}$. The magnitude of the derivative of $\bar{h}$ with respect to $\bar{r}$, $f$, represents the channel size distribution.
A mean channel size can also be calculated from the first moment of the $f$.

### 2025-03-14 chapters/paper1.tex
Changes 1. Added more visualizations of data 2. Added some images of analysis techniques in use 3. Fixed referencing to some images in aims 1,2,3

However, for the spherical particles this local topology change
disappears once the spinodal decomposition ceases, observed as a
convergence of all curvatures. This is not observed for the bijels
stabilized by ellipsoidal particles. Despite all our curvature
calculations being normalized with their surface area to volume ratio,
we still see curvature differences as a function of the applied magnetic
field. Experiments have identified that curvature changes can occur due
to the formation of monogels, which are particle networks formed from
bijels that can withstand the remixing of their constituent liquids.
\cite{sanz_colloidal_2009, lee_making_2013} This process cannot occur in
our simulations as we are utilizing repulsive particles. Therefore, the
change in curvature arises from the differences in local state of the
colloids at the interface.

@@

To measure the particle alignment quantitatively, we computed the
nematic order tensor using the method detailed in Section \ref{section:nematic_order_parameter} 
Figure \ref{fig:nematic_time} shows the time evolution of the nematic
order parameter \(S\) for the three different particle aspect ratios
\(\alpha\) and varying magnetic field strength \(\bar{B}\). The onset of
orientational order is nearly instantaneous and increases with
increasing field strength. For magnetic flux densities
\(\bar{B}\ge0.5\), the nematic order parameter saturates at
\(S\approx 1.0\) towards the end of the simulation. For the prolate
particles (\(\alpha=2.0\)), we observe a shoulder at around
\(10^4\Delta t\) and an intermittent plateau. The occurrence of this
plateau coincides with the slowed decay of the coarsening speed in Fig.
\ref{fig:coarsening_velocity}. This change in the orientational ordering
is even more distinct for the oblate particles, where the nematic order
decays intermittently before it increases again. The intermittent decay
for oblate particles, and the plateau for prolate particles, correlate
with the delayed onset of jamming in the direction perpendicular and
parallel to the magnetic field, respectively. These observations can be
interpreted as follows: The magnetic field aligns the particles with the
direction of the magnetic field early during the simulation. Due to this
alignment, the steric constraints between particles adsorbed at the
interface are reduced which allows further coarsening of the interfacial
area. However, during coarsening, the interfaces may re-orient
themselves and cause a capillary torque on the particles that competes
with the magnetic torque. This competition intermittently perturbs the
nematic order of the particles leading to the observed decay and plateau
of the nematic order parameter. Accordingly, the decay of \(S\) is most
pronounced at the weakest magnetic field \(\bar{B}=0.2\).

To further corroborate this mechanism, we quantify the orientational
order of the interfaces. We computed the interfacial orientation tensor
%
\begin{equation}
\tens{Q}_{\text{int}} = \frac{1}{\langle \mathrm{tr}(\tens{A}) \rangle} 
\left\langle \tens{A} - \frac{1}{3} \mathrm{tr}(\tens{A}) \mathsf{1} \right\rangle ,
\end{equation}
%
where the local tensor field $\tens{A}$ is defined by
%
\begin{equation}
\tens{A} = \nabla\phi\otimes\nabla\phi .
\end{equation}
%
The largest eigenvalue of $\tens{Q}$ is taken as the
interface nematic order parameter $S_{\text{int}}$.

@@

For both types of anisotropic particles, the average angle between the
particle dipole and the interface normal is initially around
\(\psi\approx60^\circ\). As the spinodal interface sweeps through the
system, particles attach to the interface and alignment due to the
capillary torque sets in. For oblate particles, the dipole axis aligns
with the interface normal as indicated by the decay of \(\psi\) towards
zero. For prolate particles, the preferential alignment of the dipole
axis is parallel to the interface and hence \(\psi\) increases towards
\(90^\circ\). The main variation of \(\psi\) occur in a time interval
around \(10^4\Delta t\) which coincides with the distinct features of
the coarsening speed and the particle nematic order observed above. The
results thus substantiate the proposed mechanism of particle
re-orientation in the magnetic field and the concomitant local alignment
of the interface. Once the particles start jamming, the shrinking
interfacial area forces some particles out of their preferred alignment
with the interface, leading to an increase of \(\psi\) for oblate
particles and a decrease of \(\psi\) for prolate particles. Figure
\ref{fig:psi_time} suggests that the forced tilting is more pronounced
for oblate particles than for prolate particles. Due to the larger
aspect ratio, the tilting of prolate particles relative to the interface
induces deformations that appear to cause a larger capillary torque than
the tilting of oblate particles. %For oblate particles, the liquid-solid
%contact line is on average further away from the particle center than
%for prolate particles, hence the lever effect of oblate particles is
%weaker and allows larger tilting relative to the the preferred alignment
%with the interface.
Hence the prolate particles remain mostly aligned with the interface
even in the stronger applied magnetic fields.

Information on the average ordering of the particles towards a
direction can be characterized using the nematic order parameter.
\cite{veerman_phase_1992, gunther_timescales_2014} However, we would
like to understand the local ordering of the particles over time. We
utilize the 6 fold Steinhardt order parameter Q6.
\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013} 
This parameter has been used extensively to characterize nucleation
rates, glass transitions of colloidal systems and crystal structure
transitions of ceramics and colloidal crystals.
\cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007}
The original implementation has been further improved through the use an
averaged bond order parameter, adding the next nearest neighbor to the
neighbor list or utilizing voronoi cells to define the neighbor list
instead of a cutoff distance. The latter provides the more robust
implementation of the bond order parameter and is implemented in the
package Freud. \cite{ramasubramani_freud_2020} This method has been used
to characterize the jamming of discs at interfaces.
\cite{ozawa_jamming_2012} We select \(Q6\) as the parameter to calculate
due to the hexagonal ordering seen in the visualizations of the particle
monolayer. We plot the averaged bond order parameter for each timestep,
\(\langle Q6 \rangle\) calculated using a neighbor list derived from
voronoi cells below.

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{figures/results/paper1/steinhardt_vs_coverage.png} 
    \caption{Time dependence of the mean two and six fold symmetry parameter, $\langle Q2 \rangle$ and $\langle Q6 \rangle$ 
    for bijels stabilized with oblate(left), spherical(middle) and prolate(right) particles. We use $\langle Q2 \rangle$ as an
    indicator of global particle translational order while $\langle Q6 \rangle$ is an indicator of local order.} 
    \label{fig:Q6_coverage} 
\end{figure}

From Figure \ref{fig:Q6_coverage}, we observe that
\(\langle Q6 \rangle \approx 0.34\) for all systems before increasing.
For bijels stabilized with spherical particles, we observe that
\(\langle Q6 \rangle\) monotonically increases until
\(\langle Q6 \rangle \approx 0.485\), indicating that the spherical
particles reach a hexagonally arranged state at the interface upon
jamming. In contrast, oblate and prolate particles respectively at the
\(t = 10^5\) timesteps have values \(\langle Q6 \rangle \approx 0.44\)
and \(\langle Q6 \rangle \approx 0.35\) respectively, indicating that
the arrangement of colloids on the interface are not hexagonal close
packed. We can verify these observations in the visualizations in
Figures \ref{fig:microstructure_viz}

We observe a magnetic field dependent increase in \(\langle Q6 \rangle\)
for prolate particles to \(\langle Q6 \rangle \approx 0.4\) and decrease
for oblate particles to \(\langle Q6 \rangle \approx 0.42\). As the
magnetic field strength is increased, we observed the interface
possessed a more negative gaussian curvature. Previous work by Cavallaro
et al.~demonstrated that surfaces with large gaussian curvature
gradients can be utilized to control particle self assembly at
interfaces owing to the excess interfacial energy induced by the
curvature gradient. \cite{cavallaro_curvature-driven_2011} Spherical
particles have monopolar effects which for the colloid sizes we are
modelling are negligible. Previous literature has also ascertained
aspect ratio dependent self-assembly of ellipsoids. We attribute the
changes in the local ordering to be due to aspect ratio dependent self
assembly, amplified by the greater curvature gradient present upon
application of a magnetic field. Next, we analyze how these local
toplogical changes affect the microstructure of the bijel by analyzing
the width of the domains in the bijel.

>>>>

However, for the spherical particles this local topology change
disappears once the spinodal decomposition ceases, observed as a
convergence of all curvatures. This is not observed for the bijels
stabilized by ellipsoidal particles. Despite all our curvature
calculations being normalized with their surface area to volume ratio,
we still see curvature differences as a function of the applied magnetic
field. Experiments have identified that curvature changes can occur due
to the formation of monogels, which are particle networks formed from
bijels that can withstand the remixing of their constituent liquids.
\cite{sanz_colloidal_2009, lee_making_2013} This process cannot occur in
our simulations as we are utilizing repulsive particles. Therefore, the
change in curvature arises from the differences in local state of the
colloids at the interface. From the microstructure results in Figures \ref{fig:D2a_B}
in addition to the genus differences characterized in Figure \ref{fig:curvature_vs_coverage},
the connectivity of the microstructure is affected through the application of magnetic fields.
We can use the channel size distribution to investigate how the connectivity of the microstructure and thus the 
channel size is affected as a function of the applied magnetic field.

While minor run to run variation is observed, the combined data of the channel size distribution shown in Figure \ref{fig:CSD_B_ss} shows some major differences 
in the channel size distribution in each bijel stabilized with oblate particles. It was expected that the domain anisotropy obtained using second moment of the 
structure factor would manifest as two peaks in the channel size distribution. \cite{karthikeyan_formation_2024} This behavior is observed in the channel size 
distribution for bijels stabilized with oblate and prolate particles with $\bar{B} = 1$, but is more difficult to see when smaller magnetic fields are applied. 
We see that there is a shift to larger channel sizes upon application of the magnetic field for bijels stabilized by ellipsoids. These differences arise from the 
particle ordering and local distribution changes observed.

\begin{figure} 
        \centering 
        \includegraphics[scale = 0.4]{figures/results/paper1/CSD_ss.png} 
        \caption{Plots of the channel size distribution for bijels stabilized by oblate, spherical and oblate particles at the final timestep plotted
                 against the distance from the interface normalized with the characteristic length scale. The channel sizes obtained are averaged over 
                 three runs. We see that the peak locations are shifted to larger and smaller positions for bijels stabilized with ellipsoidal particles
                 upon field application} 
        \label{fig:CSD_B_ss}
    \end{figure}

@@

To measure the particle alignment quantitatively, we computed the
nematic order tensor using the method detailed in Section \ref{section:nematic_order_parameter} 
Figure \ref{fig:nematic_time} shows the time evolution of the nematic
order parameter \(S\) for the three different particle aspect ratios
\(\alpha\) and varying magnetic field strength \(\bar{B}\). The onset of
orientational order is nearly instantaneous and increases with
increasing field strength. For magnetic flux densities
\(\bar{B}\ge0.5\), the nematic order parameter saturates at
\(S\approx 1.0\) towards the end of the simulation. For the prolate
particles (\(\alpha=2.0\)), we observe a shoulder at around
\(10^4\Delta t\) and an intermittent plateau. The occurrence of this
plateau coincides with the slowed decay of the coarsening speed in Fig.
\ref{fig:coarsening_velocity}. This change in the orientational ordering
is even more distinct for the oblate particles, where the nematic order
decays intermittently before it increases again. The intermittent decay
for oblate particles, and the plateau for prolate particles, correlate
with the delayed onset of jamming in the direction perpendicular and
parallel to the magnetic field, respectively. These observations can be
interpreted as follows: The magnetic field aligns the particles with the
direction of the magnetic field early during the simulation. Due to this
alignment, the steric constraints between particles adsorbed at the
interface are reduced which allows further coarsening of the interfacial
area. However, during coarsening, the interfaces may re-orient
themselves and cause a capillary torque on the particles that competes
with the magnetic torque. This competition intermittently perturbs the
nematic order of the particles leading to the observed decay and plateau
of the nematic order parameter. Accordingly, the decay of \(S\) is most
pronounced at the weakest magnetic field \(\bar{B}=0.2\). To further corroborate 
this mechanism, we plot the time evolution of the orientational order of the interfaces.

@@

For both types of anisotropic particles, the average angle between the
particle dipole and the interface normal is initially around
\(\psi\approx60^\circ\). As the spinodal interface sweeps through the
system, particles attach to the interface and alignment due to the
capillary torque sets in. For oblate particles, the dipole axis aligns
with the interface normal as indicated by the decay of \(\psi\) towards
zero. For prolate particles, the preferential alignment of the dipole
axis is parallel to the interface and hence \(\psi\) increases towards
\(90^\circ\). The main variation of \(\psi\) occur in a time interval
around \(10^4\Delta t\) which coincides with the distinct features of
the coarsening speed and the particle nematic order observed above. The
results thus substantiate the proposed mechanism of particle
re-orientation in the magnetic field and the concomitant local alignment
of the interface. Once the particles start jamming, the shrinking
interfacial area forces some particles out of their preferred alignment
with the interface, leading to an increase of \(\psi\) for oblate
particles and a decrease of \(\psi\) for prolate particles. Figure
\ref{fig:psi_time} suggests that the forced tilting is more pronounced
for oblate particles than for prolate particles. Due to the larger
aspect ratio, the tilting of prolate particles relative to the interface
induces deformations that appear to cause a larger capillary torque than
the tilting of oblate particles. %For oblate particles, the liquid-solid
%contact line is on average further away from the particle center than
%for prolate particles, hence the lever effect of oblate particles is
%weaker and allows larger tilting relative to the the preferred alignment
%with the interface.
Hence the prolate particles remain mostly aligned with the interface
even in the stronger applied magnetic fields. We plot the interface angle of bijels
stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
that the application of magnetic fields have on the particle monolayer.

\begin{figure}
        \centering
        \includegraphics[scale = 0.4]{figures/results/paper1/psi_concat.png}
        \caption{Visualizations of the particle monolayer at the last timestep shaded with the interface angle of each particle in red. The top and bottom
                 rows correspond to snapshots of bijels with no field and a field strength of $\bar{B} = 1$ applied. We see that the oblate particles flip
                 out of the interface into a non energetically favored position while the bijels stabilized with prolate particles tilt out of the interface
                 but are less likely to flip out.}
        \label{fig:psi_viz_ss}
\end{figure}

From Figure \ref{fig:psi_viz_ss} we can see the differences in the particle alignment to the interface characerizing the differences in $\psi$ observed. Oblate
particles can be seen to tilt out of the interface more readily than prolate particles at the same magnetic field strength. Due to the strong surface tension
between the fluids, the particles are strongly adsorbed onto the interface. We also see that the arrangement of particles on the interface is modified through the
application of the magnetic field for both particle morphologies. We can obtain quantitative metrics regarding this ordering using the Steinhardt 2 and 6 fold
order parameters, $\langle Q2 \rangle$ and $\langle Q6 \rangle$.

This parameter has been used extensively to characterize nucleation rates, glass transitions of colloidal systems and crystal structure transitions of ceramics 
and colloidal crystals. \cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007} The original implementation has been further 
improved through the use an averaged bond order parameter, adding the next nearest neighbor to the neighbor list or utilizing voronoi cells to define the 
neighbor list instead of a cutoff distance. The latter provides a more robust definition of the neighbor list, without needing to assume the structure of 
the particles and is implemented in the package Freud. \cite{ramasubramani_freud_2020} This method has been used to characterize the jamming of discs at 
interfaces. \cite{ozawa_jamming_2012}

We select $\langle Q6 \rangle$ and $\langle Q2 \rangle$ as the bond order parameters to calculate as we are interested in identifying the point when ordering 
of the material changes. Kapfer et al. demonstrated that only using $\langle Q6 \rangle$ to identify the ordering of particles in the system can result in 
false positives when the particles have icosahedral or amorphous structure. \cite{kapfer_jammed_2012} Mickel et al. showed how increasing deviations from 
$\langle Q2 \rangle = 0$ can be used to characterize increasing disorder in a system. \cite{mickel_shortcomings_2013} By plotting $\langle Q6 \rangle$ and 
$\langle Q2 \rangle$, we will be able to identify changes in the local ordering of the system even if we cannot directly assess the local structure.

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{figures/results/paper1/steinhardt_vs_coverage.png} 
    \caption{Time dependence of the mean two and six fold symmetry parameter, $\langle Q2 \rangle$ and $\langle Q6 \rangle$ 
    for bijels stabilized with oblate(left), spherical(middle) and prolate(right) particles. We use $\langle Q2 \rangle$ as an
    indicator of global particle translational order while $\langle Q6 \rangle$ is an indicator of local order.} 
    \label{fig:steinhardt_coverage} 
\end{figure}

From Figure \ref{fig:steinhardt_coverage}, we see an increase in disorder in all the bijel systems characterized as an increase in $\langle Q2 \rangle$. 
This is a characteristic of how the particles were initialized and move once the simulation is initiated. The particles are initialized to be randomly placed 
in the simulation domain with roughly equal spacing. As the interface sweeps through the simulation domain, particles irreversibly adsorb onto the interface 
and move with the interface until the bijel jams. We see that $\langle Q2 \rangle$ is magnetic field dependent for oblate particles but not for the spherical 
and prolate particles. We also see an aspect ratio dependence on the values characterized as differences in the time evolution of $\langle Q2 \rangle$. This 
arises due to the differences in the aspect ratio of the particle causing them to arrange differently on the interface as the bijel microstructure evolves.

An increase in $\langle Q6 \rangle$ can indicate an increase in the number of particles adopting icosahedral symmetry at the interface of the amorphous 
interface. \cite{kapfer_jammed_2012} However due to the amorphous nature of the arrangement of particles at the particle monolayer, we use this parameter 
only to gauge changes in local arrangements of particles at the interface and make no commentary on specific interfacial arrangements. For oblate particles, 
we characterize a reduction in local order as the applied field strength is increased, consistent with the increase in $\langle Q2 \rangle$. For prolate 
particles, we observe that $\langle Q6 \rangle$ increases with the applied field. This indicates that the application of the field causes particles to have 
increased local order, even if we see no discernible changes in $\langle Q2 \rangle$.

The application of the magnetic field affects the prolate and oblate particle differently due to their aspect ratio. At interfaces, rod-like particles 
prefer to orient themselves in an end to end fashion. \cite{eatson_capillary_2023} Disc-like particles have been shown to prefer stacking. \cite{dabat_mesoscale_2018} 
Application of the magnetic field and the presence of an interface will constrain the rotation of the particles, meaning that naturally rods will pack better at 
interfaces than discs as the magnetic field causes the particles to align to the field. This better packing at the interface manifests as greater local ordering 
Next, we analyze how these local toplogical changes affect the microstructure of the bijel by analyzing the channel size distribution of the bijels.

### 2025-03-14 chapters/paper2.tex
Changes 1. Added more visualizations of data 2. Added some images of analysis techniques in use 3. Fixed referencing to some images in aims 1,2,3

When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
begins at $10 ^{\circ}$.We see $\langle \psi \rangle$ decrease slightly, before plateauing and slowly increasing again. The rate of decrease in 
$\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
small compared to bijels stabilized with oblate particles. We believe this is due to local particle effects at the interface. We probe this by identifying 
the local particle ordering at the interface characterized by $\langle Q6 \rangle$.

>>>>

When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
begins at $10 ^{\circ}$.We see $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
$\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
small compared to bijels stabilized with oblate particles. We visualize this process by color coding snapshots of the particle monolayer at the initial
and final timesteps of bijels stabilized by prolate particles with a field strength of $\bar{B} = 1$ applied.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.4]{../figures/results/paper2/psi_concat_startB-0_endB-1.png} 
    \caption{Visualizations of bijel stabilized by ellipsoidal particles made with no applied field having a field strength of $\bar{B} = 1$ applied. The top and bottom 
             rows show $\psi$ for each particle at the initial and final timesteps respectively.The intensity
             of the red color qualitatively indicates the magnitude of the $\psi$ for each particle. Field application causes particles to flip out of the interface for
             oblate particles, while prolate particles tilt out of the interface. The interface is shaded with the Gaussian curvature.} 
    \label{fig:psi_field_on_visualize} 
\end{figure}

From the visualizations in Figure \ref{fig:psi_field_on_visualize}, we see that the particles lie mostly flat on the interface at the initial timestep for bijels
stabilized with oblate and prolate particles. Upon application of a field strength of $\bar{B} = 1$, we observe that the particles in the snapshot at the final timestep 
are in different conformations for bijels stabilized with oblate and prolate particles. Oblate particles tend to flip on the interface into a metastable state where
the interface covered by each particle is done with the $R_p$ and $R_o$ compared to its lowest energy state where it lies flat with radii $R_o$. The particle monolayer
of bijels stabilized by prolate particles tilt out of the interface with no metastable configurations observed. This effect explains the trends seen in $\langle \psi \rangle$
at long times for both particle morphologies. This particle flipping on the interface affects the way the particles can arrange on the interface. We probe this by identifying 
the local particle ordering at the interface characterized by $\langle Q6 \rangle$.

### 2025-03-14 chapters/paper3.tex
Changes 1. Added more visualizations of data 2. Added some images of analysis techniques in use 3. Fixed referencing to some images in aims 1,2,3

We show in Table \ref{table:rheology_fit} that the application of magnetic fields makes the bijel rheological behavior more Newtonian for both particle 
morphologies. We also see that bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices than bijel templates made with no
applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian. We also characterize that the yield stress 
of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. The yield stress of 
bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, we 
characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. We 
showed that as magnetic fields were applied, oblate particles have lower local ordering on the interface while for prolate particles it increases.
Past investigations have identified that particle monolayers buckle more easily as local particle ordering decreases. \cite{prakash_buckling_2024} 
They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
In the following sections, we will investigate the magnetic field process and the effect of local particle ordering on the microstructure of the bijel.

>>>>

We show in Table \ref{table:rheology_fit} that the application of magnetic fields makes the bijel rheological behavior more Newtonian for both particle 
morphologies. We also see that bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices than bijel templates made with no
applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian. We also characterize that the yield stress 
of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. The yield stress of 
bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, we 
characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. We 
showed that as magnetic fields were applied, oblate particles have lower local ordering on the interface while for prolate particles it increases.
Past investigations have identified that particle monolayers buckle more easily as local particle ordering decreases. \cite{prakash_buckling_2024} 
They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
We visualize the ordering of the particles at the interface to the z direction for both particle morphologies at $Ca_s = 10^{-6}$ for the 
case $\bar{B}: 1 \rightarrow 0$.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.4]{../figures/results/paper3/tz_concat_startB-1_endB-0.png} 
    \caption{Visualization of the particle monolayer of bijels stabilized by prolate and oblate ellipsoidal particles with processing history $\bar{B}: 1 \rightarrow 0$
             undergoing an applied shear of $Ca_s = 10^{-6}$. Particles with a deeper purple shade have a larger angle to the z axis. The top row shows the initial 
             configuration of the particles while the bottom row shows the final configuration of the particles. } 
    \label{fig:particle_viz_tz} 
\end{figure}

In Figure \ref{fig:particle_viz_tz}, we see that the particle are initially ordered to the direction of the applied magnetic field. Upon application of shear and removal
of the magnetic field, we see that the particles begin reorienting away from the z direction. We also observe that the reorientation of particles uncovers the interface.
The reorientation observed is particle morphology specific with prolate particles seeing more reorientation away from the applied shear direction than oblate particles.
Looking at the images, we see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
while oblate particles reorient towards minimizing area to the applied shear direction.In the following sections, we will investigate the microstructural implications of
the uncovering of the bijel interface, in addition to understanding more about the particle reorientation at the interface and its effects.
